An Extensible Approach to Verification of Embedded Systems

### 2014-05-02 tech-project/related_works_and_conclusion.tex

Though RESOLVE is the only system we know of that proves, prior to compilation, the full functional correctness of embedded software, there are a number of other systems that 
%There are a number of existing systems that ultimately seek to prove the functional correctness of programs. While we discuss only two here, readers interested in learning more about the systems mentioned might to refer to \cite{klebanov:2011} for a more in depth discussion. Perhaps most notable among the systems we list here (and perhaps the closest to RESOLVE's approach) is Microsoft research's Dafny \cite{leino:2010}. Designed to be capable of verifying pointer based structures, Dafny currently stands as one of the more popular approaches to verification. Substituting RESOLVE's notion of mathematical variables with what are termed `ghost' variables, reasoning is kept, like RESOLVE, disconnected from implementation-level code. Dafny uses an intermediate verification language, termed Boogie, to generate verification conditions which are then dispatched via Z3, Microsoft's automated prover.

@@

Using embedded application development as an example, we perceive this work as a step towards more fully exploring the role of formal verification in lower level system-oriented contexts. Indeed, the realm of embedded systems provides an ideal stepping off point for this challenge, as it encourages (and indeed, requires) RESOLVE to provide support for not only new target languages (namely C), but also new language constructs that give the user the ability to author drivers required for any serious embedded application. While we have made progress with the latter in the form of the externally keyword, a natural direction for future work would entail using RESOLVE's performance specification mechanisms to prove the time and duration estimates for a memory allocator, not unlike the one presented here. Indeed, by being able to prove aspects of this system at this level of granularity (down to time and space) confidence in the systems we rely upon everyday (embedded systems included)

proving memory and time constraints on any allocation scheme will provide assurance that we never exceed limitations or behave unexpectedly.

Moreover, if we do In the future if we do it dynamically or statically there is no difference, if the static people are concerned about memory, the It might not seem like we're doing much w

>>>>

There are a number of existing systems and techniques geared towards verification of embedded programs written in C. While we discuss only a handful here, readers interested in learning more about the systems and approaches mentioned are encouraged to refer to the references provided for each.

The first approach, bounded model checking, is the main focus of the work detailed in \ref{cordeiro:2009}.

%Though RESOLVE is the only system we know of that proves, prior to compilation, the full functional correctness of embedded software, there are a number of other systems that

@@

Using embedded application development as an example, we perceive this work as a step towards more fully exploring the role of formal verification in lower level system-oriented contexts. Indeed, the realm of embedded systems provides an ideal stepping off point for this challenge, as it encourages (and indeed, requires) RESOLVE to provide support for not only new target languages (namely C), but also new language constructs that give the user the ability to author drivers required for any serious embedded application. While we have made progress with the latter in the form of the externally keyword, a natural direction for future work would entail using RESOLVE's performance specification mechanisms to prove the time and duration estimates for a memory allocator, not unlike the one presented here. Indeed, by being able to prove aspects of this system at time and space level granularity, the question of whether our programs will exhaust stack space becomes a non-issue, as we will be assured -- prior to execution -- that we are within the systems limitations.
